Pillar 2 - Topic Modeling

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd
delets Griffths2004

  dtm = data_cast,
  topics = n_topics,
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

@@

```{r manual topics, cache = TRUE}
start.time <- Sys.time()

@@

```{r LDA number topics plot}

@@

result_description %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

result_overview %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

result_manual %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

@@

```{r LDA fit, cache = TRUE}
n_topics <- 35
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

>>>>

  dtm = data_cast,
  topics = n_topics,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

@@

We run the test for manuals, documenting its duration.
```{r manual topics, cache = TRUE}
start.time <- Sys.time()

@@

We examine the result of the experiment by plotting them on a graph.
```{r LDA number topics plot}

@@

result_description %>%
  FindTopicsNumber_plot

result_overview %>%
  FindTopicsNumber_plot

result_manual %>%
  FindTopicsNumber_plot

@@

From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics.
```{r LDA fit, cache = TRUE}
n_topics <- 35
levels   <- c("description", "overview", "manual")
list_nam <- character(0)
